%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/AnkitRajCode}{\Huge Ankit Raj}} &  \href{https://github.com/AnkitRajCode}{github.com/ankitrajcode}\\
  \textbf{Purnea, Bihar} & \href{https://www.linkedin.com/in/ankitrajcode}{linkedin.com/in/ankitrajcode} \\
  Ph. : \href{tel:+919661134518}{+91 9661134518} & Email : \href{rajankit432@gmail.com}{rajankit432@gmail.com} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://kiit.ac.in/}{Kalinga Institute of Industrial Technology}}{Bhubaneshwar, India}
      {BTech in Information Technology;  \href{}{CGPA: 8.95}}{July. 2019 -- June. 2023}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\textbf{Coursework}{: Data Structure \&\ Algorithms, OOPs Concept, Problem Solving, DBMS, SDLC.} \\
 	\textbf{Languages/Frameworks}{: C/C++, Java, HTML/CSS, JavaScript, NodeJs, ExpressJs, ReactJs, NextJs.} \\
 		\textbf{Database}{: MongoDB, Firebase}\\
 		\textbf{Tools}{: Git, Linux, Visual Studio Code, Eclipse, Figma.}\\
	}}
 \end{itemize}
 \vspace{-16pt}
 
 %

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {\href{https://www.linkedin.com/company/opentext/}{OpenText}}{Bengaluru, India}
      {Intern}{Jan. 2023 - Present}
      \resumeItemListStart
        \resumeItem{}{Utilized \textbf{Agile} methodology to \textbf{Develop} monthly reports for OCC team Using a Spring Boot application.}        
        \resumeItem{}{Implemented \textbf{REST API} calls to retrieve necessary data for report generation.}
        \resumeItem{}{Automated the previously manual process of counting data across multiple Excel files and individual profiles, resulting in a \textbf{15 - 20 hr/week reduction} in debugging and setup time.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://www.linkedin.com/company/epikindifi/}{EPIKInDiFi}}{Bhubaneswar, India}
      {Intern Trainee}{Jan. 2022 - Jun. 2022}
      \resumeItemListStart
        \resumeItem{}{Gained \textbf{hands-on} experience in \textbf{ReactJS, JavaScript, EDA, and Linux} through training and mentorship.}
        \resumeItem{}{Developed baseline knowledge of software, applications, and technical processes within creating mobile applications, and website functionality using \textbf{ReactJs} and \textbf{JavaScript}.}
        \resumeItem{}{Utilized EDA tools to improve efficiency and gained experience working with \textbf{Linux} operating systems.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
     \resumeSubheading{\href{https://www.codedynamics.in/}{Code Dynamics}}{{\href{https://github.com/AnkitRajCode/CodeDynamics}{- Source Code}}}{Figma, NextJs, Tailwind CSS, Strapi (CMS), GIT, and hosted on Vercel (.in domain)}{}
      \resumeItemListStart
        \resumeItem{}{Code Dynamics project provides DSA solutions for major platforms, including 30K+ solutions, 50+ RRS, and optimized solutions for all programming languages.}
        \resumeItem{}{The project includes a Dynamics sheet for the DSA community and has 150+ users during pre-launch.}
        \resumeItem{}{The web app is dynamic and being made PWA-compatible for easy access.}
    \resumeItemListEnd
    
    \resumeSubheading{\href{https://nextgenui.in}{Next Gen UI}}{{\href{https://github.com/AnkitRajCode/Component-UI}{- Source Code}}}{Dynamic and Intuitive Component Library}{}
      \resumeItemListStart
        \resumeItem{}{Created a dynamic and intuitive component library with a vast collection of web components (navbar, footer, cards, buttons, etc.) using NextJs, Tailwind CSS, and Firebase.}
        \resumeItem{}{Built the library with a focus on simplicity and ease of use by providing code in HTML and React and pursuing the goal of converting it into an NPM package.}
        \resumeItem{}{Included \textbf{dynamic routing} in the library to enable seamless navigation between the different components.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------Achievements-----------
\section{Achievements}
%  \begin{itemize}[leftmargin=0.15in, label={}]
% 	\resumeItemListStart
 \resumeSubHeadingListStart
    	\resumeItem{}{I was Web Dev. Lead at \href{https://gfgkiit.netlify.app/}{\bf GeeksforGeeks KIIT}}
    	
    	\resumeItem{}{Earned \textbf{5*} Badge in \textbf{C, C++ and DSA},  4* in \textbf{Python}, and completed \textbf{30 Days of Code} on  {\href{https://www.hackerrank.com/satyajeetramnit1?hr_r=1}{\bf Hackerrank.}}}
%   	\resumeItemListEnd
 \resumeSubHeadingListEnd
%  \end{itemize}
%  \vspace{-16pt}
 %
 

%-----------Certifications & Profile Links-----------
\section{Certifications and Profile Links}
 \begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
		\href{https://www.hackerrank.com/certificates/8c1ecb8ffd40}{\textbf{Problem Solving, NodeJs, ReactJs, SQL, CSS and Python} (Hackerrank Certifications)} \\
 	    \href{https://www.udemy.com/certificate/UC-ccf367dd-b692-405e-94c2-b67eeebd693d/}{\textbf{Linux Command Line} (Udemy)} \\
      \href{https://drive.google.com/file/d/16q_hy_uXJ3_Wx2DnA3NZALC5zqLaSTZs/view}{\textbf{Full Stack MERN Bootcamp} (LearnCodeOnline)} \\
 	    \href{https://drive.google.com/file/d/1TTGRI2AzBL_3gYKKtnOnh9yId2DWm_5P/view}{\textbf{GeeksforGeeks KIIT Lead}{ Dept. Web Development}} \\
 	    \  \ \\
 	    \textbf{Profile Links :}{ $|$ \href{https://leetcode.com/AnkitRajCodes/}{{Leetcode}} $|$ \href{https://www.hackerrank.com/AnkitRajCodes}{{Hackerrank}} $|$ \href{https://github.com/AnkitRajCode}{{Github}} $|$ \href{https://ankitraj.pages.dev}{{Portfolio}} $|$} \\
	}}
 \end{itemize}
 \vspace{-16pt}
 
%-------------------------------------------
\end{document}